The `geomnet` package

### 2017-04-05 README.Rmd
plotly ex

>>>>

## Interactivity with `plotly`!

Now including interactivity with `ggplotly()`!

```{r football, eval = FALSE}
library(geomnet)
# devtools::install_github("ropensci/plotly")
library(plotly)
data(blood)
bloodnet <- fortify(as.edgedf(blood$edges), blood$vertices)
p <- ggplot(data = bloodnet, aes(from_id = from_id, to_id = to_id))

# create data plot
p2 <- p + geom_net(aes(size=Predominance, colour=type, shape=rho, linetype=group_to),
             linewidth=0.75, labelon =TRUE, directed = TRUE, labelcolour="black") +
  facet_wrap(~Ethnicity) +
  scale_colour_brewer(palette="Set2") 
ggplotly(p2)
```
